How has the Brazilian Amazon been constructed as a problem? An analysis of

### 2022-04-07 Draft_April_2022/Full_draft_20220401.rmd
#text corrections

Our findings are threefold. First, endogenous events as the death of Chico Mendes, the 1992 Earth Summit, the 2009 Copenhaguen Summit, the 2015 Paris Summit, and the 2021 London Summit drive generally the interest in the Amazon. That seems to be the case even after controling share of annual speeches mentioning the Amazon for deforestation, inflation, and speaker. Second, there was a sharp decrease in economic related problem-constructions from the late 1990 to 2010, matched by an increase in speeches that construct the Amazon as a problem of social development and environmental conservation. This trend is reversed in the late 2010s, with the twist of sovereignty making a strong comeback. Finally, using a multinominal model, we find that the farthest away the speaker is from the Amazon, be it within the country in non-Amazonian States or outside Brazil, the more likely the speaker is to construct the Amazon as a problem of environmental conservation than economic integration or social development.

@@

As we move from a world where non-state actors gain importance in environmental governance and international politics generally [@silva-muller2022; @andonova2014; @westerwinter2021], the sovereignty problem becomes more varied. Multiple non-state actors (NGOs, foundations, IOs, and so on) join the conversation about Amazonian policies more substantially as the military dictatorship starts to end [@hochstetler2021; @capobianco2019; @franchini2019]. Threads to national sovereignty, consequently, can be interpreted as coming from a different set of actors than before. Allegedly false claims about the Brazilian Amazon in international and domestic fora, for instance, are often tied to strategies of 'internationalizing' the Amazon. This might come both from foreign actors as well as domestic non-state actors. Relatedly, mentions of Amazonian myths which have been debunked as the 'Earth of the Lungs', are also tied to internationalizing strategies

@@

This section presents the three main findings of our analysis. We open with a broad overview of the evolution of the incidence of Amazon in all presidential speeches since 1985. In section 4.2, we focus on speeches that mention the Amazon, introducing the specific problem-constructions we presented in section 2.1. Finally, we run a multinominal model to show how problem constructions change as the speaker moves further away from the Amazon region.

>>>>

Our findings are threefold. First, endogenous events as the death of Chico Mendes, the 1992 Earth Summit, the 2009 Copenhaguen Summit, the 2015 Paris Summit, and the 2021 London Summit drive generally the interest in the Amazon. That seems to be the case even after controlling share of annual speeches mentioning the Amazon for deforestation, inflation, and speaker. Second, there was a sharp decrease in economic related problem-constructions from the late 1990 to 2010, matched by an increase in speeches that construct the Amazon as a problem of social development and environmental conservation. This trend is reversed in the late 2010s, with the twist of sovereignty making a strong comeback. Finally, using a multinominal model, we find that the farthest away the speaker is from the Amazon, be it within the country in non-Amazonian States or outside Brazil, the more likely the speaker is to construct the Amazon as a problem of environmental conservation than economic integration or social development.

@@

As we move from a world where non-state actors gain importance in environmental governance and international politics generally [@silva-muller2022; @andonova2014; @westerwinter2021], the sovereignty problem becomes more varied. Multiple non-state actors (NGOs, foundations, IOs, and so on) join the conversation about Amazonian policies more substantially as the military dictatorship starts to end [@hochstetler2021; @capobianco2019; @franchini2019]. Threads to national sovereignty, consequently, can be interpreted as coming from a different set of actors than before. Allegedly false claims about the Brazilian Amazon in international and domestic fora, for instance, are often tied to strategies of 'internationalizing' the Amazon. This might come both from foreign actors as well as domestic non-state actors. Relatedly, mentions of Amazonian myths which have been debunked as the 'Earth of the Lungs', are also tied to internationalizing strategies.

@@

This section presents the three main findings of our analysis. We open with a broad overview of the evolution of the incidence of Amazon in all presidential speeches since 1985. In section 4.2, we focus on speeches that mention the Amazon, introducing the specific problem-constructions we presented in section 2.1. Finally, we run a multinomial model to show how problem constructions change as the speaker moves further away from the Amazon region.
